---
title: "Regression Plots"
format: html
editor: visual
---

```{r setup, include=F}
knitr::opts_chunk$set(warning=F, error=F, message=F)
```

```{r load-libraries, include=F}
library(performance)
library(see)
library(ggplot2)
library(ggthemes)
```

## Regression Plots

```{r}
lm <- lm(mpg ~ hp * wt, data = mtcars)
```

## Default Plots

```{r}
par(mfrow = c(2, 2))
plot(lm)
```

## Performance Plots

### Default Performance Plot

```{r new, out.width="100%", fig.height=8}
performance::check_model(lm, theme = "see::theme_lucid")
```

### Theme Minimal

```{r theme-minimal, out.width="100%", fig.height=8}
performance::check_model(lm, theme = "ggplot2::theme_minimal")
```

### Theme Tufte

```{r theme-tufte, out.width="100%", fig.height=8}
performance::check_model(lm, theme = "ggthemes::theme_tufte()",
                         colors = c("#C87A8A", "#6B9D59", "#5F96C2"))
```

## Check Normality

```{r}
check_normality(lm)
```

To better understand the function, run `?performance::check_normality()`.

## Check Heteroskedacity

```{r}
check_heteroskedasticity(lm)
```

To better understand the function, run `?performance::check_heteroskedasticity()`.

## Challenges

The `themes` argument did not work, `colors` argument did.

## Acknowledgements

Many thanks to Dr. Lyndon Walker for his tutorial on youtube. His channel can be found [here](https://www.youtube.com/@DrLyndonWalker).
